Accelerated Inference for Partially Observed Markov Processes using Automatic Differentiation

### 2024-07-19 paper/ms.tex
Updates from Overleaf

\begin{figure}[t!]
    \centering
    \includegraphics[width=\arxiv{\textwidth/\real{1.25}}{\textwidth/\real{2.5}}]{imgs/pmcmc/nuts_eb.png}
    \arxiv{}{\vspace*{-1mm}}
    \caption{Convergence diagnostics for NUTS with the informative nonparametric empirical Bayes prior from applying KDE to preliminary searches using IF2, with $4$ chains. We display the results for the trend parameter in the Dhaka cholera model of \cite{king08}. NUTS mixes quickly, and the posterior estimates from each chain share roughly the same posterior mode.}
    \label{fig:nuts-eb}
    \arxiv{}{\vspace*{-4mm}}
\end{figure}

@@

While the result is presented here as specific to MOP-$\alpha$, we prove a more general result in \arxiv{Appendix~\ref{appendix:targeting}}{the supplementary material}.
This is a strong law of large numbers for triangular arrays of particles resampled according to an arbitrary resampling rule not necessarily in proportion to the targeted distribution of interest, to weights that encode the cumulative discrepancy between the resampling and the target distribution.

>>>>

\begin{figure}[t!]
    \centering
    \includegraphics[width=\arxiv{\textwidth/\real{1.25}}{\textwidth/\real{2.5}}]{imgs/pmcmc/nuts_eb.png}
    \arxiv{}{\vspace*{-1mm}}
    \caption{Convergence diagnostics for NUTS when estimating $\beta_{\text{trend}}$ with the informative nonparametric empirical Bayes prior from applying KDE to preliminary searches using IF2, with $4$ chains. NUTS mixes quickly, and the posterior estimates from each chain share roughly the same posterior mode.}
    \label{fig:nuts-eb}
    \arxiv{}{\vspace*{-4mm}}
\end{figure}

@@

While the result is presented here as specific to MOP-$\alpha$, we prove a more general result in \arxiv{Appendix~\ref{appendix:targeting}}{the supplementary material}.
This is a strong law of large numbers for triangular arrays of particles resampled arbitrarily, with resampling probabilities not proportion to the targeted distribution of interest, to weights that correct for the cumulative discrepancy between the resampling and the target distribution.
